---
title: "StockWatch"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
  html_document:
    theme: flatly
---
```{r echo=FALSE, message=FALSE, warning=FALSE}
library(quantmod)
library(dplyr)
library(purrr)
library(here)
library(TTR)
library(ggplot2)
library(plotly)
library(blastula)
library(DT)
library(data.table)
library(fontawesome)
library(lubridate)
library(PerformanceAnalytics)

# proj functions
source(here("01_reports", "fn", "functions.R"))

# Get a nicely formatted date/time string
date_time <- add_readable_time()

# detail crosswalk
cx <- read.csv(here("00_data", "nasdaq_screener.csv")) 

```
Good Morning: This is a daily review of the stocks in your portfolio, updated on `r date_time`.

```{r echo=FALSE, message=FALSE, warning=FALSE}

symbols <- c("HOOD", "BBAI", "HIMS", "ONDS", "BULL",
             "MSTR", "BTBT", "ACHR", "TMC", "SPY",
             "UNH", "MSTY", "UTI", "TGT", "NET",
             "CHWY", "QBTS", "RGTI", "NFLX", "ON",
             "ULTY", "CMG","JOBY", "PANW","FIG",
             "HOVR", "AMD", "DIS", "SHOP", "IONQ", "RDDT")

port_symbols <- c("AAPL", "COST", "CRCL", "ELF", "JPM", "GOOGL", "AMZN", "GLD", "NET", "VUG", "MSFT", "NVDA", "VOO", "BYDDY", "V", "VDADX", "QQQM", "QQQ", "VYM", "SCHD", "O", "TSM", "BABA", "VDE", "NBIS", "GELYF", "BA", "EL", "TCMD", "CRWV")

symbols <- sort(symbols)

getStockData <- function(sym){
  tryCatch(
    {quantmod::getSymbols(sym, src='yahoo', from="2024-01-02", auto.assign=FALSE)}, error = function(msg){
    return(NA)})
  }

# gather list of stocks 
stock_df <- map(symbols, ~getStockData(.x))

# remove stocks w/o data
no_data <- which(is.na(stock_df))
ne_data <- which(map(stock_df, ~nrow(.x)<7) == TRUE)
rm_stock <- c(no_data, ne_data)
if(!is_empty(rm_stock)){
  stock_df <- stock_df[-rm_stock]
  symbols  <- symbols[-rm_stock] 
}
names(stock_df) <- symbols

# stack data
main_df <- map_df(
  symbols,
  ~clean_data(.x, data = stock_df)
) 

constructs <-  main_df %>% add_constructs()
  

# backtest strategy (1 year of data) 
bt_data  <- constructs %>% filter(date >= today() - 730)
backtest <- split(bt_data, bt_data$stock) %>% map(backtest_strategy)
bt_subset <- do.call("rbind", backtest) %>% slice_max(date) %>% select(stock, signal, execute)

# eval and plot backtesting results
bt_eval <- map(backtest, eval_strategy)
bt_plots <- map(backtest, plot_strategy)

split_df <- split(constructs, constructs$stock)
list_infl <- map(symbols, ~get_inflections(.x, df = split_df))
names(list_infl) <- symbols

# finalize
constructs <- constructs %>% 
  slice_max(date) %>% 
  left_join(bt_subset, by = c("stock"))

date_of_data <- constructs$date[1]
```

Market data as of `r date_of_data`.     

---

##  {.tabset}

### Summary Table
```{r echo=FALSE, message=FALSE, warning=FALSE}

constructs %>% 
  mutate(
    delta_volume = ifelse(dod_vol > 0, fa(name = "arrow-up", fill = "green"), 
                   ifelse(dod_vol < 0, fa(name = "arrow-down", fill = "red"), ""))
    ) %>% 
  select(
    "Symbol" = stock, 
    Close, 
    DoD, 
    WoW, 
    MoM, 
    YoY, 
    "Volume Chg" = delta_volume, 
    "Trend"      = trend, 
    "Signal"     = signal
    ) %>% 
  DT::datatable(
    escape = FALSE,
    options = list(pageLength = 50, autoWidth = TRUE)
  ) %>% 
  DT::formatStyle(
    c("DoD", "WoW", "MoM", "YoY"),
    backgroundColor = DT::styleInterval(0, c('pink', 'lightgreen'))
    ) %>%
  DT::formatStyle(
    c("Signal"),
    backgroundColor = DT::styleEqual(c('Buy', 'Sell', 'Neutral'), c('green', 'orange', 'lightgrey'))
    ) %>% 
  DT::formatPercentage(c("DoD", "WoW", "MoM", "YoY"),1) %>% 
  DT::formatRound(c("Close"), 2)
```

### Charts {.tabset}
```{r, echo=FALSE, results='asis', message=FALSE, warning = FALSE}

imls_slides <- lapply(symbols, function(x) {
  knitr::knit_child(text = c('',
    '#### `r x` {.tabset}',
    '##### `r x` Strategy',
    '```{r, echo=FALSE, fig.width=8, fig.height=8, message=FALSE, warning = FALSE}',
    'bt_plots[[x]]',
    'bt_eval[[x]]',
    '```',
    '##### `r x` Static 2mo',
    '```{r, echo=FALSE, fig.width=8, fig.height=8, message=FALSE, warning = FALSE}',
    'plot_stock(x, data = stock_df, time = "last 2 month")',
    '```',
    '##### `r x` Static 1yr',
    '```{r, echo=FALSE, fig.width=8, fig.height=8, message=FALSE, warning = FALSE}',
    'plot_stock(x, data = stock_df, time = "last 1 year")',
    '```',
    ''
  ), envir = environment(), quiet = TRUE)
})
cat(unlist(imls_slides), sep = '\n')
```


