---
title: "Portfolio of Stocks"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: html_document
---
```{r echo=FALSE, message=FALSE, warning=FALSE}
library(quantmod)
library(dplyr)
library(purrr)
library(here)
library(TTR)
library(ggplot2)
library(plotly)
library(blastula)
library(DT)
library(fontawesome)

# proj functions
source(here("VisualizeStocks", "fn", "functions.R"))

# Get a nicely formatted date/time string
date_time <- add_readable_time()

# detail crosswalk
cx <- read.csv(here("VisualizeStocks", "Data", "nasdaq_screener.csv"))
```
Good Morning: This is a daily review of the stocks in your portfolio, updated on `r date_time`. The data is lagged by ~1 day.

---
```{r echo=FALSE, message=FALSE, warning=FALSE}

symbols <- c("AAPL", "COST", "JPM", "GOOGL", "AMZN", "BGSAX", "NET", "VUG", "MSFT", "PRWCX", "NVDA", "DODGX", "PRGTX", "VOO", "VEIRX", "VTSAX", "BYDDY", "VWILX", "V", "VDADX", "QQQM", "QQQ", "VYM", "SCHD", "O", "TSM", "BABA", "VDE", "NBIS", "GELYF", "BA", "EL", "TCMD", "CRWV")


symbols <- sort(symbols)

# gather list of stocks 
stock_df <- map(symbols, ~getSymbols(.x, src='yahoo', from="2023-01-02", auto.assign=FALSE))
names(stock_df) <- symbols

# stack data
main_df <- map_df(
  symbols,
  ~clean_data(.x, data = stock_df)
) 

constructs <-  main_df %>% 
  group_by(stock) %>% 
  mutate(
    # --- Volume Calculations --- 
    sma_vol   = TTR::EMA(Volume, n = 7),
    diff_vol   = sma_vol- lag(sma_vol, 7) ,
    pct_vol  = (diff_vol/lag(sma_vol, 7) - 1) * 100,
    
    # --- Price Averages ---
    ema_close  = TTR::EMA(Close, n = 7),
    pct_emavg = (ema_close/lag(ema_close, 7) - 1) * 100,
    
    # --- Price Changes ---
    # Daily 
    diff_prev  = Close- lag(Close) ,
    DayOverDay  = (diff_prev/abs(lag(Close))),
    
    # Weekly
    diff_week  = Close- lag(Close, 7) ,
    WeekOverWeek  = (diff_week/abs(lag(Close, 7))),
    
    # Monthly
    diff_month = Close- lag(Close, 30) ,
    MonthOverMonth = (diff_month/abs(lag(Close, 30)))
    
  ) %>% 
  ungroup() %>% 
  left_join(
    cx,
    by = c("stock" = "Symbol")
  )
  

split_df <- split(constructs, constructs$stock)
list_infl <- map(symbols, ~get_inflections(.x, df = split_df))
names(list_infl) <- symbols

```
##  {.tabset}

### Summary Table
```{r echo=FALSE, message=FALSE, warning=FALSE}
constructs %>% 
  slice_max(date) %>% 
  mutate(
    delta_volume = ifelse(pct_vol > 0, fa(name = "arrow-up", fill = "green"), 
                  ifelse(pct_vol < 0, fa(name = "arrow-down", fill = "red"), "")),
    delta_close  = ifelse(pct_emavg > 0, fa(name = "arrow-up", fill = "green"), 
                  ifelse(pct_emavg < 0, fa(name = "arrow-down", fill = "red"), ""))
    ) %>% 
  select(stock, Close, DayOverDay, WeekOverWeek, MonthOverMonth, delta_volume, delta_close) %>% 
  DT::datatable(
    escape = FALSE,
    options = list(pageLength = 30, autoWidth = TRUE)
  ) %>% 
  DT::formatStyle(
    c("DayOverDay", "WeekOverWeek", "MonthOverMonth"),
    backgroundColor = DT::styleInterval(0, c('pink', 'lightgreen'))
    ) %>% 
  DT::formatPercentage(c("DayOverDay", "WeekOverWeek", "MonthOverMonth"),1) %>% 
  DT::formatRound(c("Close"), 2)

```

### Charts {.tabset}
```{r, echo=FALSE, results='asis'}

imls_slides <- lapply(symbols, function(x) {
  knitr::knit_child(text = c('',
    '#### `r x` {.tabset}',
    '##### `r x` Static 2mo',
    '```{r, echo=FALSE, fig.width=8, fig.height=8, message=FALSE}',
    'plot_stock(x, data = stock_df, time = "last 2 month")',
    '```',
    '##### `r x`Static 1yr',
    '```{r, echo=FALSE, fig.width=8, fig.height=8, message=FALSE}',
    'plot_stock(x, data = stock_df, time = "last 1 year")',
    '```',
    '##### `r x` Interactive',
    '```{r, echo=FALSE, fig.width=8, fig.height=8, message=FALSE}',
    'plotly_stock(x, data = split_df)',
    '```',
    ''
  ), envir = environment(), quiet = TRUE)
})
cat(unlist(imls_slides), sep = '\n')
```

